Open Science, Open Plant Pathology

### 2020-04-23 analysis/paper/paper.Rmd
Update paper with recent changes to scoring

A general workflow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, and writing the manuscript.
Here we defined three levels of reproducibility which are also related with the evolution of computational methods and reproducible practices \@ref(fig:workflow-dia).

@@

In order for us to determine where we are as a discipline with regards to openly and reproducibly sharing data, we randomly selected 300 articles published from 2012 to 2018 across 21 journals (Table \@ref(tab:journals)) representative of the pathology discipline, and assigned them scores reflecting their openness and reproducibility.
Among the journals, both fundamental and/or applied as well as journals covering specific group of pathogens/plants or broad areas were included.
Three hundred articles were randomly selected from issues published from 2012 to 2018.
A list of randomly selected pages was assigned to a randomized list of the 21 journals [@Sparks2017] where the page number fell within an article for the given journal.
In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
Notes regarding the selection of articles can be found in the file, XXXX, available in this paper's repository.
The pages list was numbered from page one and went to 150.
This was done since some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published, since most journals start with page number one at the beginning of the year.
The list of journals was saved from Google's gsheets as a comma separated value (CSV) file for later use and distribution.

@@

Journals were provided a score for whether they were completely open (TRUE), behind a pay wall (FALSE) or a combination (BOTH).
The five-year impact factor for 2018 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
This was downloaded, saved as a .csv file and is left-joined with the article notes using `dplyr::left_join()` for analysis when the `import_notes()` command is executed.

Articles were provided classifications, whether they were fundamental or applied and a note was made whether the article's primary focus was molecular (TRUE/FALSE).
This classification was based on the evaluator's own judgement of the article.

Further classification as to whether the articles focused on using or developing molecular techniques was included.

Where possible the software used was recorded in the notes if it was cited or otherwise specified in the article text.

@@

@@

    * 3 - All software components (SAS PROCs, R or Python packages) etc. cited

@@

@@

The majority of the articles were classed as fundamental, 160, with 138 classed as applied.

@@

The majority of articles scored very low in our reproducibility assessment, 82.6&nbsp;% scored 0 out of 12, which was not reproducible at all (Table \@ref(tab:reproducibility)).
The highest scoring article received an 11 out of 12.

>>>>

A general workflow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, and writing the manuscript.
Here we defined three levels of reproducibility which are also related with the evolution of computational methods and reproducible practices (Figure \@ref(fig:workflow-dia)).

@@

In order for us to determine where we are as a discipline with regards to sharing openly and reproducible papers and data, we randomly selected 300 articles published from 2012 to 2018 across 21 journals (Table \@ref(tab:journals)) representative of the pathology discipline, and assigned them scores reflecting their openness and reproducibility.
The journals represented both fundamental and applied areas as well as pathogen or other group specific publications.
Three hundred articles were randomly selected from issues published from 2012 to 2018.
A list of randomly selected pages was assigned to a randomized list of the 21 journals where the page number fell within an article for the given journal.
In cases where an article was not suitable, _e.g._, a review or otherwise not related to plant pathology, the next article was selected until a suitable article was found.
Notes regarding the selection of articles can be found in the file, XXXX, available in this paper's repository.
The pages list was numbered from page one and went to page 150.
This was done since some journals restart their numbering with each issue and also ensures that the journal is more likely to have a page number corresponding to the randomly generated value.
This also assumes that there is no effect or bias on reproducibility based on the time of year that an article was published, since most journals start with page number one at the beginning of the year.
The list of journals was saved from Google's gsheets as a comma separated value (CSV) file for later use and distribution in a research compendium.

@@

Each journals was classified as to  whether they were completely open (TRUE), behind a pay wall (FALSE) or a combination (BOTH).
The five-year impact factor for 2018 for each journal was retrieved from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
This was downloaded, saved as a CSV file and is left-joined with the article notes using `dplyr::left_join()` for analysis when the `import_notes()` command is executed.

Articles were classified as fundamental or applied and a note was made whether the article's primary focus was using or developing molecular techniques (TRUE/FALSE).
This classification was based on the evaluator's own judgement of the article.

Where possible, the software used in the preparation of the publication was recorded in the notes if it was cited or otherwise specified in the article text.

@@

    * 1 - Uses expensive proprietary software that only institutions would typically purchase (_i.e._, 
    ArcGIS standard is $7000US)

    * 2 - Uses proprietary software that most individuals can afford (_e.g._, Excel) or SAS that is now available free for use with a univerisity login

@@

    * 3 - All software components (SAS PROCs, R or Python packages) etc., cited

@@

A total reproducibility score was calculated as the percent of total possible for a given paper,
_e.g._ some papers did not use specialized software therefore they were not scored for this category.

@@

The majority of the articles were classed as fundamental, 160, with the remaining 138 classed as applied.

@@

Forty-eight articles scored 0&nbsp;% out of a possible 100&nbsp;% for reproducibility.
The mean value was 31.2&nbsp;% and the median value was 33.3&nbsp;%.
One article scored 100&nbsp;%, or was classed as fully reproducible.
